Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-11-23 metanalysis_visualization/visualization.Rmd
pvalues bootstrap calculation

```{r}
outputDir <- "../../output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
getwd()
```

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
  }else{
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, table1, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, length_hospitalisation_values)
}
```

@@

>>>>

```{r}
outputDir <- "../output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
  print(i)
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
  }else{
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <-  rbind( bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <-  rbind( bootstrapped_coefficients_all, bootstrapped_coefficients_df)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, table1, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, length_hospitalisation_values)
}
```

@@

### Total number of patients per month an site

```{r}
patients_hospitalized_agg_sex_perc_all %>%
  select( time_p, count, siteid) %>%
  unique() %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date) %>%
  ggplot(aes(x = time_p, y = count, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "number of patients",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Total number of patients with mental disorders per site \n ( per ", time_period,")"))
```

## Boostrap vizualisation
```{r}
# bootstrap_size <- 1000
# binom_proportion <- function(n, prob, size) {
#   (rbinom(n, size, prob) / size) * 100
# }
# 
# # View(patient_count_psy_period_psy_all)
# 
# bootstrap_function <- function(df, ...) {
#   bootstrapped_timepoints <- mapply(binom_proportion,
#          n = bootstrap_size,
#          size = df$count_no_psy_patients +
#            df$count_psy_patients,
#          prob = df$percentage/100)
#   
#   bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
#   bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
#   for (iteration in 1:bootstrap_size) {
#   df_iteration <- data.frame(period = df$period,
#                              time = df$time,
#                              percentage = bootstrapped_timepoints[iteration, ])
#   ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
#   linear_model <- broom::tidy(ts_linear_percent) %>%
#     filter(term %in% c("time", "periodduring_pandemic:time"))
#   coefficients <- linear_model$estimate
#   names(coefficients) <- linear_model$term
#   bootstrapped_coefficients_list[[iteration]] <- coefficients
#   df_iteration$predicted <- predict(ts_linear_percent)
#   df_iteration$time_p <- df$time_p
#   bootstrapped_sample_list[[iteration]] <- df_iteration
#   }
#   bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")
#   bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list, .id = "iteration")
#   list("bootstrapped_fitted_df" = bootstrapped_fitted_df,
#        "bootstrapped_coefficients_df" = bootstrapped_coefficients_df)
# }
# 
# 
# bootstrapped_all <- patient_count_psy_period_psy_all %>% 
#   group_by(siteid) %>% 
#   group_map(bootstrap_function) %>% 
#   set_names(nm = names_site_id)
# 
# bootstrapped_fitted_all <- purrr::map(bootstrapped_all, "bootstrapped_fitted_df") %>% 
#   bind_rows(.id = "siteid")
# bootstrapped_coefficients_all <- purrr::map(bootstrapped_all, "bootstrapped_coefficients_df") %>% 
#   bind_rows(.id = "siteid")

names_site_id <- unique(patient_count_psy_period_psy_all$siteid)

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = quantile(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

annotation_function <- function(df, ...) {
  pvalue_coeff_interaction <- round(
    (1- max(
      sum(df[["periodduring_pandemic:time"]] > 0,
          df[["periodduring_pandemic:time"]] < 0)
    )/nrow(df)) * 2
    , 3) 
  paste0("Coeffs differences: ",
                      round(mean(df[["periodduring_pandemic:time"]]), 2),
                      " (pvalue: ",
                      pvalue_coeff_interaction,
                      ")")
}

plot_annotations <- bootstrapped_coefficients_all %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf, y = +Inf, hjust=0, vjust=1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

### 2021-11-23 psy_peds_3.Rmd
pvalues bootstrap calculation

bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list, .id = "iteration")
mean(bootstrapped_coefficients_df$time)
mean(bootstrapped_coefficients_df$time + bootstrapped_coefficients_df[["periodduring_pandemic:time"]])
pvalue_coeff_interaction <- round(t.test(bootstrapped_coefficients_df[["periodduring_pandemic:time"]])$p.value, 4)
plot_annotation <- paste0("Diff. in slope coeffs before and after pandemic: ",
                     round(mean(bootstrapped_coefficients_df[["periodduring_pandemic:time"]]), 2),
                     " (pvalue: ",
                     pvalue_coeff_interaction,
                     ")")

>>>>

bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list, .id = "iteration")
mean(bootstrapped_coefficients_df$time)
mean(bootstrapped_coefficients_df$time + bootstrapped_coefficients_df[["periodduring_pandemic:time"]])

pvalue_coeff_interaction <- round(
  (1- max(
    sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] > 0,
        bootstrapped_coefficients_df[["periodduring_pandemic:time"]] < 0)
  )/nrow(df)) * 2
  , 3)

plot_annotation <- paste0("Coeffs differences: ",
       round(mean(bootstrapped_coefficients_df[["periodduring_pandemic:time"]]), 2),
       " (pvalue: ",
       pvalue_coeff_interaction,
       ")")
